The \dealii Library, Version 9.5

### 2023-05-22 9.5/paper.tex
Update the Trilinos section.

We have added a new wrapper to \texttt{Belos}. The package
\texttt{Belos}  is the
successor of \texttt{AztecOO} and provides basic and advanced iterative solvers
that heavily rely on multivector operations. The interface of the
wrapper is similar to the one of the native iterative solvers
provided by \dealii:

\begin{c++}
TrilinosWrappers::SolverBelos<VectorType> solver(/*...*/);
solver.solve(matrix, x, r, preconditioner);
\end{c++}

Via additional data, the user can select the actual iterative
solver to be used and set its configurations.

Furthermore, we have added a wrapper to \texttt{NOX}. This is a
nonlinear-solver library similar to \texttt{KINSOL} from \texttt{SUNDIALS}
and to \texttt{SNES} from \texttt{PETSc}. The basic interface
of the \texttt{NOX} wrapper is similar to the one of the other wrappers
mentioned before:

\begin{c++}
TrilinosWrappers::NOXSolver<VectorType> solver(/*...*/);

solver.residual            = [ ](const auto &src, auto &dst) {/*...*/};
solver.setup_jacobian      = [&](const auto &src) {/*...*/};
solver.apply_jacobian      = [&](const auto &src, auto &dst) {/*...*/};
solver.solve_with_jacobian = 
  [&](const auto &src, auto &dst, const auto tol) {/*...*/};

@@

>>>>

Trilinos is a large collection of individual sub-packages. \dealii{}
has long had interfaces to the Trilinos packages that provide parallel
vector and matrix classes (both \texttt{Epetra} and \texttt{Tpetra}),
as well as a small number of linear algebra packages for iterative
solvers and preconditions. In the current release, there are now also
interfaces to two additional packages: \texttt{Belos} and \texttt{NOX}.

\texttt{Belos} is the
successor of the Trilinos package \texttt{AztecOO} and provides basic and advanced iterative solvers
that heavily rely on multivector operations. The interface of the
wrapper is similar to \dealii{}'s own iterative solvers:
\begin{c++}
TrilinosWrappers::SolverBelos<VectorType> solver(/*...*/);
solver.solve(matrix, x, r, preconditioner);
\end{c++}
The omitted constructor arguments allow selecting the actual iterative
solver to be used, along with other configuration options.

Secondly, we have added a wrapper to \texttt{NOX}, a
nonlinear solver library similar to the \texttt{KINSOL} solver from
the \texttt{SUNDIALS} package to which we already had interfaces, as
well as to \texttt{SNES} from \texttt{PETSc} (see also
Section~\ref{sec:petsc}). The interfaces to these three solvers are
essentially the same and require setting function objects for
computing the residual of the nonlinear problem, along with setting
up, applying, and solving with the Jacobian matrix:
\begin{c++}
TrilinosWrappers::NOXSolver<VectorType> solver(/*...*/);

solver.residual            = [ ](const VectorType &src,
                                 VectorType       &dst) {/*...*/};
solver.setup_jacobian      = [&](const VectorType &src) {/*...*/};
solver.apply_jacobian      = [&](const VectorType &src,
                                 VectorType       &dst) {/*...*/};
solver.solve_with_jacobian = [&](const VectorType &src,
                                 VectorType       &dst,
                                 const double      tol) {/*...*/};

@@

\todo[inline]{I don't understand this last sentence. Can you
  elaborate? At least in the KINSOL interfaces, you only update the
  preconditioner whenever setup\_jacobian() is called.}
